### 2011-01-31 trunk/papers/webist2011/paper_sec_wrapping.tex
figure 3 back to landscape mode, but better quality
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1226 d8b0c59b-6544-0410-94d9-83a5658a058e
finally fig. 3 in good quality!!
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1227 d8b0c59b-6544-0410-94d9-83a5658a058e
after using some magic spells, the paper is back to good quality images and six pages
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1228 d8b0c59b-6544-0410-94d9-83a5658a058e

In this section we illustrate the interaction with RESTful services on simple GET requests\footnote{Other methods such as POST or SOAP-based services are also supported.}. 
In this case, a service request is assembled using its URL and a set of parameters. As an example, we will look at the eBay Shopping web service. 
To define the desired pre-condition and the type of post-condition of a new service wrapper, the service wrapper tool provides a form (not shown here). For the current example, we assume that the user has defined a pre-condition \emph{search\_key}.

We are invoking the service to retrieve a list of items corresponding to the search keyword ``USB'':

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{images/ServiceWrapperToolGVSWithRequestExample.png}
    \caption{Constructing the service request}
    \label{fig:construct_service_request}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{images/ServiceWrapperToolGVSWithTransformationRules.png}
    \caption{Rule-based transformation of service response}
    \label{fig:response_service_execution}
  \end{center}
\end{figure}

>>>>

We now illustrate the interaction with RESTful services on simple GET requests\footnote{Other methods such as POST or SOAP-based services are also supported.}. 
In this case, a service request is assembled using its URL and a set of parameters. As an example, we will look at the eBay Shopping web service. 
To define the desired pre-condition and the type of post-condition of a new service wrapper, the service wrapper tool provides a form (not shown here). For the current example, we assume that the user has defined a pre-condition \emph{search\_key}.
We are invoking the service to retrieve a list of items corresponding to the search keyword ``USB'':

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=\linewidth]{images/ServiceWrapperToolGVSWithRequestExample.png}
    \caption{Constructing the service request}
    \label{fig:construct_service_request}
  \end{center}
\end{figure}

@@

\begin{figure}[hb]
  \begin{center}     
    \includegraphics[width=\linewidth]{images/ServiceWrapperToolGVSWithTransformationRules-HQ.png}
    \caption{Rule-based transformation of service response}
    \label{fig:response_service_execution}
  \end{center}
\end{figure}
